\documentclass[8pt,a4paper,sans]{moderncv}
\usepackage{verbatim}
\moderncvstyle{classic}
%\moderncvstyle{banking}
%\moderncvstyle{casual}
%\moderncvstyle{fancy}
%\moderncvstyle{oldstyle}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\firstname{Petru}
\familyname{Marginean}
\address{16 Ridgecrest East}{Scarsdale, NY 10583}
\mobile{(914)365-0326}
\email{petru.marginean@gmail.com}
\homepage{github.com/petrum}  

\begin{document}
\maketitle
\section{Profile}
\cvlistitem{Expert C++ developer with +20 years of experience}
\cvlistitem{Petru started coding as a teenager on a ZX Spectrum clone in 1985.
  He discovered the assembler language on the Z80 processor,
  and then he taught himself coding using Pascal, and the C language.
  In 1992 he was programming using C++ on IBM PC.
  Upon graduating college he got a job programming financial applications using FoxPro.
  In 1995 he started using C++ profesionally at a Romanian-American startup company writing Windows applications using COM/OLE.
  In 1998 Petru moved to the US, and continued writing applications using C++ for top US companies.
  In 2002 he transitioned to Linux environment helping Bear Stearns to port their C++ risk system from Sun Solaris to Linux.
  He continued to work full-time for different investment banks until 2011 when he switched to the buy side.}
\cvlistitem{Experience with building execution systems for trading Equity, Futures, and Options}
\cvlistitem{Proficient in Python/Pandas, Perl, Q/kdb+, Sybase/SQL, Excel/VBA, Java, PHP, C\#}
\cvlistitem{Worked in the financial industry for +14 years}
\cvlistitem{Coding standards, logging, error handling and testing are very much addressed because of their importance
  (please see below articles that cover these important aspects of programming)}

\section{Publications}

\cventry{Nov 2009}{Logging in C++ Part 2}{Dr. Dobb's Journal}{}{C++ article}
        {\textit{Each individual logging statement can be conveniently turned on and off without the need
            to recompile or even stop and restart the application}}

\cventry{Jul 2008}{Lock-Free Queues}{Dr. Dobb's Journal}{}{C++ article}
        {\textit{I present a lock-free queue in which one thread can write to the queue and another read from it
            at the same time without any locking}}

\cventry{Sep 2007}{Logging in C++ Part 1}{Dr. Dobb's Journal}{}{C++ article}
        {\textit{Logging is a critical technique for troubleshooting and maintaining software systems.
            Petru presents a C++ logging framework that is type-safe, thread-safe, and portable}}

\cventry{Jun 2003}{Generic<Programming>: Enforcements}{Dr. Dobb's Journal}{in co-authorship with Andrei Alexandrescu}
        {C++ article}
        {\textit{You gotta love writing error-handling code - you know, all the joy of testing conventions and
            formatting strings and throwing exceptions and... This is no joke. After you read "Enforcements"
            maybe you'll agree: error handling can be fun. The inimitable duo of ScopeGuard fame hits again,
            this time to take the boredom away from error-handling code}}
 
\cventry{Dec 2000}{Generic<Programming>: Change the Way You Write Exception-Safe Code; Forever}{Dr. Dobb's Journal}
        {C++ article}{in co-authorship with Andrei Alexandrescu}
        {\textit{Let's face it: writing exception-safe code is hard. But it just got a lot easier with this amazing template}}

\cventry{Feb 1999}{Communication Between Browsers Using RMI}{Dr. Dobb's Journal}
        {Java article}{}
        {\textit{Remote method invocation can help offset some of the limitations on Java applets imposed in the name of security.}}

\section{US Working Experience}

\cventry{Aug 2011- Today}{IT Director, Execution Services}{Laurion Capital Management}{New York City}{}
        {The main developer of the C++ execution system used for trading for Equities, Futures by more than +20 traders. 
          Designed, implemented, and supports very low latency execution system using Redline API (Inrush + EG).
          Developed from scratch option execution system, and risk monitor using the SpiderRock SRSE interface (Python/Pandas).
          Developed from scratch C\# order monitor, and a C++ order entry using QT library.
          Also designed and developed STP system (Perl) that retrieves real-time executions from
          different execution brokers (options, FX, equities, futures, SWAPS) and books them into the Imagine risk system.
          Developed Perl modules for reconciliation broker files with Geneva accounting system.}

\cventry {May 2007- Aug 2011}{VP Fixed Income}{Morgan Stanley}{New York City}{}
         {Lead of development team for Interest Rates electronic trading system (Virtual Markets).
           The VirtualMarkets (VM) allows traders to trade over multiple markets (Btec, Espeed, CME,
           Govex, ELX, NyseLiffe, Eurex, Liffe) using a simple, and consistent interface. 
           VM offers virtualization of the markets that have similar instruments (Cash OTR on BTEC/Espeed/Govex or
           Futures on CME/ELX/NyseLiffe).
           VM allows traders to create strategies (Switches, Packs, Index) for automatic trading.
           VM displays different stats about the markets, such as Hi/Lo/Last, bucketed volumes, trade history,
           participation (both MS and non-MS), volumes at price.
           Responsible for extending VM for new markets, bug fixes, coordinating releases (economic events),
           adding new features at the request of traders.
           Designed and implemented C++ market data application supporting the Government, Agencies, and Mortgages
           desks; low latency, high performance.
           Extensive experience with Ion Trading C API (used to connect to the all markets).
           Designed and implemented state-of-the-art logging system (see articles in Dr. Dobb's).
           Designed and implemented highly efficient lock free queue (see article).
           Designed and implemented Kdb+/Q ticker plant to replace existing Sybase server.
           Created Perl tools for monitoring the application performance, error detection, automatic graph generation.}

\cventry{Jun 2005- May 2007}{VP Equity Derivatives}{Banc of America Securities LLC}{New York City}{}
        {Front-office developer for the ``Risk Engine'' team.
          Redesigned and developed from scratch a high performance C++ application to calculate the prices for virtually
          any security, including all the Greeks.
          Worked very closely with Quants.
          The application can also apply configurable scenarios (used to generates trader heat-maps, and VaR).
          It used DataSynapse to distribute the intensive calculations. It also used gSOAP to retrieve the
          input data in the XML format.
          The Xerces library was used to parse the XML and extract the data (the code compiled/run on both Windows/Linux platforms)
          Intensive use of the boost library (multi-threading, command-line options, smart pointers, tuples).
          Petru's ScopeGuard was included in the boost library.
          Extensive use of design patterns such as visitor, object factory, and singleton.
          Responsible for the full cycle of the application, from design and coding to testing, deployment, and support.
          Created a WTL GUI interface for the security pricer, for easier use on Windows.
          Experience with the C++ services model of DataSynapse, gSOAP, Xerces libraries.
          Rewrote the application that generates the P\&L with very much improving error handling,
          readability of the code, and logging}

\cventry{Nov 2002- June 2005}{Associate Director Equity Derivatives}{Bear Stearns}{New York City}{}
        {Front-office developer for the ``Structured Equity Finance'' desk.
          Lead development of a new system to price and manage the risk of barrier options, total return swaps,
          pass-through certificates (and plan to extend it to include principal-protected notes, loans and warrants)
          on the baskets of hedge funds or fund of funds.
          The system verified the compliance with various guidelines and created many client reports using Crystal Reports.
          Designed generic panels in C\# using the Syncfusion datagrid.
          Support for CFD (Contract for Differences), and Swap products.
          Developed various Excel spreadsheets (VBA) to assist the traders with different calculations.}

\cventry{Jun 2001- Nov 2002}{C++ Senior developer}{ILX Systems}{New York City}{}
        {Redesigned and implemented a complex ActiveX application that emulates a TN3270 terminal.
          This terminal emulator is part of the ActiveILX, the new ILX workstation. ActiveILX's fully
          customizable component workstation enables you to build a "workspace" that meets trader's needs. 
          Intensively use of C++ language, STL, COM/ATL.}

\cventry{Mar 1998- Jun 2001}{C++ senior developer}{Plural}{New York City}{}
        {Dell Buys Services Company Plural.
          Senior C++ developer with Java experience.
          Designed, developed and tested COM C++ components (using C++, STL, ATL, ORACLE database, ASP).
          The framework used for developing a Java client-server application became the subject of a Java article
          published in Dr. Dobb's (see above).}

\section{Education and Formal Training}
\cventry{2006}{Derivative Mathematics certificate}{New York Institute of Finance}{New York City}{}{}
\cventry{1998}{Microsoft Certified Solution Developer}{online exam}{}{renewed in 2001}{}
\cventry{1989-1994}{BS in Electrical Engineering}{University Politehnica of Bucharest}{Major in Computer Systems}{}{}

\section{Personal Projects}
\cvlanguage{sshremote}{Android app}{It helps execute remote SSH commands by pressing a button on your smartphone}
\cvlanguage{WeatherTicker}{Raspberry Pi}{It continously displays the local weather and the weather forecast}
\cvlanguage{Ding}{Raspberry Pi}{Using SDR and reverse engineering you hack your wireless door bell and you control it from
  your smartphone}
\cvlanguage{Motion}{Raspberry Pi}{It detects motion using a PIR sensor and it sends you a notification email}
        
\end{document}
